---
title: Short Paper
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    footnote: 1
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
  - name: Cat Memes
    email: cat@example.com
    affiliation: Another University
    footnote: 2
  - name: Derek Zoolander
    email: derek@example.com
    affiliation: Some Institute of Technology
    footnote: 2
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  This is the abstract.

  It consists of two paragraphs.

journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
link-citations: yes
linkcolor: blue 
urlcolor: blue
citecolor: blue
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl) # Lire un base de donnes Excel
#library(here)
```

# Introduction

<!-- Context -->
The context is important [@Dirac1953888].
for example, @Feynman1963118 say it.

<!-- Reserch problem -->
<!-- Research gap in the literature -->
<!-- Literature review -->
<!-- Purpose of the article -->

# Methodology

<!-- Presenting the methodology -->

This is the first Graph

```{r graphic1-data, include=FALSE}
# Don't show up
data.excel <- read_excel("data/Test_Attrakdiff.xls" ) 

#identifying the onglets
onglets <- excel_sheets("data/Test_Attrakdiff.xls")

# Reading the onglet that corresponds
data.excel <- read_excel("data/Test_Attrakdiff.xls",  sheet = onglets[2]) 


# Reading the onglet that corresponds
data.excel <- read_excel("data/Test_Attrakdiff.xls",  
                         sheet = onglets[2], 
                         skip = 2) 

# Selecting the corresponding rows
data.excel <- data.excel %>% slice(1:11)

# Changing names columns
col_names <- names(data.excel)
col_names[1] <- c("Participant")

names(data.excel) <- col_names
  
data.excel <- 
  data.excel %>%  select(Participant : QP7)



# Pivot_longer to analyse
data.excel <- 
  data.excel %>% pivot_longer(cols = -Participant, 
                              names_to = "Variables",
                              values_to = "Answers")



# Changing the scale of the answers
data.excel <- 
  data.excel %>% mutate( 
    change_scale =
      case_when(
        Answers == 7  ~ 3,
        Answers == 6  ~ 2,
        Answers == 5  ~ 1,
        Answers == 4  ~ 0,
        Answers == 3  ~ -1,
        Answers == 2  ~ -2,
        Answers == 1  ~ -3,
        TRUE ~ as.numeric(Answers)
      )
  )

# Changing the sign of the answers
data.excel <- 
  data.excel %>% mutate( 
    change_scale_orientation =
      case_when(
        Variables %in% 
          c("ATT1*", "ATT3*","ATT5*",
            "ATT7*", "QHI2*", "QHI3*", "QHI6*", 
            "QHS1*", "QHS3*", "QHS4*", "QP1*",
            "QP2*", "QP3*", "QP5*")  ~ as.numeric(change_scale)*(-1),
        TRUE ~ as.numeric(change_scale)
      )
  )


## Approach 2
data.excel <- 
  data.excel %>% mutate( 
    change_scale_orientation_II =
      case_when(
        str_detect(data.excel$Variables, "\\*") ~ as.numeric(change_scale)*(-1),
        TRUE ~ as.numeric(change_scale)
      ))

# Doing the Groups
data.excel <- 
  data.excel %>% mutate( 
    Factors =
      case_when(
        str_detect(data.excel$Variables, "QP") ~ "QP",
        str_detect(data.excel$Variables, "QP1") ~ "QP",
        
        str_detect(data.excel$Variables, "QHS") ~ "QHS",
        
        str_detect(data.excel$Variables, "QHI") ~ "QHI",        
        str_detect(data.excel$Variables, "QH1") ~ "QHI",        
        
        str_detect(data.excel$Variables, "ATT") ~ "ATT",
        TRUE ~ "ATTENTION"
      ))


```


```{r graphic1, include=TRUE, out.width="100%"}
data.excel %>% 
  group_by(Factors) %>% 
  summarise(Moyenne = mean(change_scale_orientation)) %>% 
  ggplot() +
  aes(y=Moyenne, x= Factors) +
  #geom_point() +
  #aes(x=Factors , y=Moyenne, group=1 ) +
  geom_bar(stat="identity", position = "dodge", lwd = 1,  aes(fill = Factors)) +
  #geom_bar(aes( stat = "identity"))
  geom_point() +
  #geom_line() +
  coord_flip() + 
  scale_x_discrete(breaks=c("ATT","QHI","QHS","QP"), 
                   labels=c("Attractivité Globale", 
                            "Qualité hédonique - Identification", 
                            "Qualité hédonique - Stimulation",
                            "Qualité Pragmatique")) +
     labs(x = "",
              y = "Level ",
              title = "Atractiff Profile",
              subtitle = paste("Total of answers:" , max(data.excel$Participant) ) ) 
```




```{r graphic2-data, include=FALSE}
# Graphique 2

# Reading the onglet that corresponds
Var_complets <- 
  read_excel("data/Test_Attrakdiff.xls",  
             sheet = onglets[5] ) %>%  
  slice(5 : 34) %>% 
  select(1:2) %>% 
  set_names (c("Variables", "Description")) %>% 
  fill(Variables) %>% 
  mutate(label = Description ) %>% 
  separate(col = Description, into = c("Left", "Right"), sep = "-") %>% 
  mutate(Factors = c( rep("QP", 7),
                      rep("QHS", 7),
                      rep("QHI", 7),
                      rep("ATT", 7)
                      ))
# Data complete

titles <- read_excel("data/Test_Attrakdiff.xls",  
                         sheet = onglets[2], skip = 1) %>% slice(1)
# Pivot long the tibble
titles <- 
  titles %>% select(2:29) %>% 
  pivot_longer(cols = everything(), names_to = "Label Incorrect", values_to = "Variables") %>% 
  separate(col = "Label Incorrect", into = c("Left", "Right"), sep = "-")

# Changing the Label
titles <- 
  titles %>% 
  mutate(
    label.correct =
      case_when(
        str_detect(Variables, "\\*") ~ paste(Right, Left, sep = " - "),
        TRUE ~ paste(Left, Right,  sep = " - ")
      ))


# Adding Factors
titles <- 
  titles %>% arrange(Variables) %>% 
  mutate(Factors = c(
    rep("ATT", 7),
    rep("QHI", 7),
    rep("QHS", 7),
    rep("QP", 7)
  ))

  
data.excel <- 
  data.excel %>% 
  left_join(titles %>% select(Variables, label.correct),
            by = "Variables")


# Ordering the dataframe
Fig2 <- 
  data.excel %>% select(Variables, label.correct, change_scale_orientation) %>% 
  group_by(Variables) %>% 
  summarise(media = mean(change_scale_orientation)) %>% 
  ungroup() %>% 
  left_join(titles,  by = "Variables") %>% 
  select(Variables, media,  label.correct, Factors) %>% 
  arrange(Factors, label.correct) 
  #mutate(label = factor(label, labels = test$label ))  # ordering factors
  
# Order Factors 
# as.factor(test$label) %>% levels(test$label)
Fig2$label.correct <- factor(Fig2$label.correct, levels = Fig2$label.correct)
```

This is the second Graph

```{r graphic2, include=TRUE,  fig.height=7, fig.width=6, out.width='100%'}
Fig2 %>%  
  ggplot(aes(x= label.correct, y= media, color = Factors, group=1 )) +
  #geom_point() +
  geom_line() +
  geom_point() +
  ggplot2::annotate("rect", xmin=c(1,8,15,22), xmax=c(7,14,21,28), 
                    ymin=rep(-3,4), ymax=rep(3, 4), 
                    alpha = .1 , fill = c("blue", "red", "grey","green")) +
  coord_flip(xlim = NULL, ylim = c(-3,5)) +
scale_y_continuous(breaks=c(-3:4), 
                 labels=c(-3:3, " ")) +
         ggplot2::annotate("text",
                           y = c(2, 2, 2, 2),
                           x = c(4, 11, 19, 26),
                           label = c("Attractivité \n globale",
                                     "Qualité \n hédonique - identification",
                                     "Qualité \n hédonique - stimulation", 
                                     "Qualité \n pragmatique"),
                           family = "Palatino", fontface = 3, size=3) +
         theme_minimal(base_size = 10, base_family = "Palatino") +
         labs(x = "",
              y = "Level ",
              title = "Atractiff Profile",
              subtitle = paste("Total of answers:" , max(data.excel$Participant) ) ) +

         theme(
            legend.position = "right",
            panel.border = element_blank(),
            panel.spacing = unit(0.1, "lines"),
            strip.text.x = element_text(size = 18, family = "Palatino")
         ) 
           

```


# Results

The Elsevier article class is based on the standard article class and
supports almost all of the functionality of that class. In addition, it
features commands and options to format the

-   document style

-   baselineskip

-   front matter

-   keywords and MSC codes

-   theorems, definitions and proofs

-   lables of enumerations

-   citation style and labeling.

# Front matter


The author names and affiliations could be formatted in two ways:

(1) Group the authors per affiliation.

(2) Use footnotes to indicate the affiliations.

See the front matter of this document for examples. You are recommended
to conform your choice to the journal you are submitting to.

# Bibliography styles

There are various bibliography styles available. You can select the
style of your choice in the preamble of this document. These styles are
Elsevier styles based on standard styles like Harvard and Vancouver.
Please use BibTeX to generate your bibliography and include DOIs
whenever available.

Here are two sample references: @Feynman1963118 [@Dirac1953888].

\newpage

# References {#references .unnumbered}

