---
title: "Biblio"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In English

* [Alison Presmanes Hill](https://twitter.com/apreshill)
* [rstudio4edu](https://rstudio4edu.github.io/rstudio4edu-book/)
* [Hadley Wickham](https://twitter.com/hadleywickham)
* [Desirée De Leon](https://twitter.com/dcossyle)
* [Yihui Xie](https://twitter.com/xieyihui)
* [Twitter for R programmers](https://www.t4rstats.com/index.html)
* [Julia Silge](https://twitter.com/juliasilge)
* [Jenny Bryan](https://twitter.com/JennyBryan)
* [Garrick Aden‑Buie](https://twitter.com/grrrck)


The R package and analysis artwork used within this book has been produced by

[allison_horst](https://twitter.com/allison_horst), whilst artwork used in information boxes has been produced by [Desirée De Leon](https://twitter.com/dcossyle). 
You can find Allison's images on the [stats illustration GitHub repository](https://github.com/allisonhorst/stats-illustrations) and Desirée's on the [rstudio4edu GitHub repository](https://github.com/rstudio4edu/rmd4edu).

I (Fabio) have certainly learnt a lot from their open code repositories!


## Bibliography on

- Goodman, Steven N., Daniele Fanelli, and John P. A. Ioannidis. 2016. “What Does Research Reproducibility Mean?” Science Translational Medicine 8 (341): 341ps12–341ps12. https://doi.org/10.1126/scitranslmed.aaf5027.


## Additional lecture for your Science 


- Chalmers, A. F., & Biezunski, M. (1990). Qu’est-ce que la science ? : récents développements en philosophie des sciences : Popper, Kuhn, Lakatos, Feyerabend. Librairie générale française.

- Sekaran, Bougie. 2016. Research Methods For Business: A Skill Building Approach. Wiley & sons.

- Sørensen, Flemming, Jan Mattsson, and Jon Sundbo. 2010. Experimental Methods in Innovation Research. Research Policy 39 (3): 313–22.




Recommended online books:

- [R for Data Science](https://r4ds.had.co.nz/)
- [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/pdf-document.html)


### Additional valuable resources {-}

You can also go through other free resources including: 

In french: 

* [Thinkr](https://thinkr.fr/)
* [Introduction à R et au tidyverse](https://juba.github.io/tidyverse/index.html)
* [analyse-R](https://larmarange.github.io/analyse-R/)



```{r}

```

In english: 


* [STAT 545](https://stat545.com/index.html#other-contributors)
* [rstudio4edu](https://rstudio4edu.github.io/rstudio4edu-book/)
* [Hadley Wickham](https://twitter.com/hadleywickham)
* [Alison Presmanes Hill](https://twitter.com/apreshill)
* [Desirée De Leon](https://twitter.com/dcossyle)
* [Yihui Xie](https://twitter.com/xieyihui)
* [Robin Lovelace](https://twitter.com/robinlovelace)
* [Twitter for R programmers](https://www.t4rstats.com/index.html)
* [Matt Ng](https://twitter.com/mattnkm)
* [StatQuest with Josh Starmer](https://www.youtube.com/channel/UCtYLUTtgS3k1Fg4y5tAhLbw)
* [Julia Silge](https://twitter.com/juliasilge)
* [Jenny Bryan](https://twitter.com/JennyBryan)
* [Garrick Aden‑Buie](https://twitter.com/grrrck)
* [Free RStudio Education resources](https://education.rstudio.com)
* [Codeacademy](https://www.codecademy.com/learn/learn-r)
* [YaRrr! The Pirate's Guide to R](https://bookdown.org/ndphillips/YaRrr/)



En Español:

* [Metadocencia](https://www.metadocencia.org/)
* [R Coder](https://r-coder.com/)




* [Free RStudio Education resources](https://education.rstudio.com)
* [Codeacademy](https://www.codecademy.com/learn/learn-r)
* [YaRrr! The Pirate's Guide to R](https://bookdown.org/ndphillips/YaRrr/)


