---
title: "Module 3: Data Wrangling in R"
subtitle: "An introduction"
author: 
  - "Fabio CRUZ"
  - "Giovanny Arbelaez"
  - "Mauricio Camargo"
institute: "ERPI"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
#output: powerpoint_presentation
output:
  xaringan::moon_reader:
    css: ["default", "css/my-theme.css", "css/my-fonts.css"]
    #css: ["assets/xaringan-themer.css"]
    seal: TRUE
    nature:
      slideNumberFormat: "%current%/%total%" 
      highlightStyle: solarized-light
      highlightLanguage: ["r", "css", "yaml"]      
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
      navigation:
        scroll: false # disable slide transitions by scrolling
always_allow_html: true
---

```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
# Source
#source("xaringan-themer.R")

# load packages ----------------------------------------------------------------
library(tidyverse)
library(xaringanExtra)
library(xaringanthemer)
library(fontawesome)
library(here)
library(countdown)
library(ymlthis)
library(tidyverse)
library(ggthemes)
library(icons) # remotes::install_github("mitchelloharawild/icons")
library(icon)
library(emoji)
library(palmerpenguins)
library(fontawesome)

options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.path = 'assets/chunks/03/', cache.path = "assets/cache/03/", 
                      collapse = TRUE,
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  fig.align = 'center',
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE,
  include = TRUE
)

# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')

#library(xaringanBuilder)
#build_pdf("index.Rmd")

# xaringanExtra
xaringanExtra::use_panelset()

#xaringanExtra::use_share_again()
xaringanExtra::use_tachyons()
xaringanExtra::use_tile_view()
xaringanExtra::use_webcam()
xaringanExtra::use_fit_screen()
xaringanExtra::use_extra_styles(hover_code_line = TRUE, mute_unhighlighted_code = TRUE)
xaringanExtra::use_share_again()
xaringanExtra::use_panelset()
```



# Modules:

1. [Basics of R & RStudio](#module1)

1. [Data Visualisation using ggplot2](#module3)

1. .bg-yellow[[Data Wrangling using dplyr](#module4)]




---

class: center, middle, inverse

# Dynamic Wrangling<br>Using dplyr


---

name: module4

class: title-slide, right, middle, hide-count, hide-logo

background-image: url("https://images.unsplash.com/photo-1591903934817-c02acbfd4665?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1932&q=80")
background-size: cover

<br>
<br>
<br>
<br>

# .black.big-text[Data<br>Wrangling]
## .black[Session - 4]

.footnote[
.white[Image credits:][Karina L](https://unsplash.com/photos/zJRQ5nngdPA)
]

---





---

class: your-turn, hide-logo

# `r emo::ji("brain")` YOUR TURN


```{r echo=FALSE}
countdown(minutes = 10, top = 0, font_size = "3em")
```

.panelset[

.panel[.panel-name[Task]

How many Chinstrap penguins are with bill length more than 45 mm and weight more than 4 kg?
]

.panel[.panel-name[Codes]

```{r yt1, eval=FALSE, echo=TRUE}
penguins %>% 
  filter(species == "Chinstrap",
         bill_length_mm > 45,
         body_mass_g > 4000) %>% 
  head()
```

]

.panel[.panel-name[Output]

```{r ref.label="yt1", echo=FALSE, message=FALSE}

```

]
]




